Survey Analysis

### 2021-09-27 1_Introduction.tex
small changes

Source code misunderstandings can occur due to many reasons; for instance, the wrong choice of names for arguments, variables, and methods might hinder developers from understanding a piece of code~\cite{avidan:icpc2017}. Besides that, programming languages can also have specific idioms and constructs that may lead to misunderstandings. That is the case of \emph{atoms of confusion}---small pieces of code that hinder developers' understanding of the source code of a program for which there are functionally equivalent alternatives that are easier to understand~\cite{DBLP:conf/sigsoft/GopsteinIYDZYC17, DBLP:conf/msr/GopsteinZFC18}.

@@

    \item A mixed-method research effort---based on a survey, interviews, and mining software repositories---about the impact of atoms of confusion on a
    dynamic language;

  \item A list of additional JavaScript-specific
    constructs and idioms that might introduce code
    misunderstanding;

>>>>

Source code misunderstandings can occur due to many reasons; for instance, the wrong choice of names for arguments, variables, and methods might hinder developers from understanding a piece of code~\cite{avidan:icpc2017}. Besides that, programming languages can also have specific idioms and constructs that may lead to misunderstandings. That is the case of atoms of confusion: small pieces of code that prevent developers from program comprehension, even though functionally equivalent alternatives exist and are easier to understand~\cite{DBLP:conf/sigsoft/GopsteinIYDZYC17, DBLP:conf/msr/GopsteinZFC18}.

@@

\item A mixed-method research effort---based on a survey, interviews, and mining software
  repositories---about the impact of atoms of confusion on JavaScript (a
    dynamic language).

  \item A comparison of the impact and prevalence of atoms of confusion in
    JavaScript with what has been previously reported for other languages
    (\clang, \cpplang, and Java).

### 2021-09-27 dataset/survey-results-final.Rmd
update the survey + spell checker
small changes

---
title: "survey-analysis-final"
output:
  pdf_document: default
  html_document: default
---

@@

library(questionr)
library(fmsb)
library(sqldf)
library(xtable)
library(effsize)
setwd(".")

## Load the datasets

@@

## Filter the datasets

@@

## Exploratory Data Analysis

@@

demEducation
barplot(demEducation$total, col=topo.colors(5), ylim = c(0, 70), cex=0.7, cex.lab = 0.7, cex.axis=0.7, ylab="Number of participants")

@@

## Regression Analysis (correctness~atom + experience + education)

@@

## Impact considering Developer Experience

@@

## Impact considering Developer Education

@@

## Impact of Individual Atoms

@@

  mod <- glm(subSet$correct ~ subSet$atom +  experience,family="binomial")
  print(summary(mod))
  print(prop.table(table(subSet$correct,subSet$experience),margin = 2))
}
analysis_df <- data.frame(atomDescription, chiTest, oddsRatio, oddsRatioTest, ci25, ci975, mannWhitneyTest, cliffDelta)
analysis_df <- analysis_df[order(-oddsRatio),]
colnames(analysis_df) <- c("Atom", "ChiTest", "Odds Ratio Correctness", "p-value", "CI 2.5%", "CI 97.5%", "Wilcox Test (Time)", "Cliff Delta")
analysis_df
xtable(analysis_df)
```

>>>>

---
title: "Survey Analysis"
output:
  html_document: default
  pdf_document: default
---

@@

library(questionr)
library(fmsb)
library(sqldf)
library(xtable)
library(effsize)
setwd(".")
```

## (1) Load the datasets

@@

## (2) Filter the datasets

@@

## (3) Exploratory Data Analysis

@@

demEducation

barplot(demEducation$total, col=topo.colors(5), 
        ylim = c(0, 70), cex=0.7, cex.lab = 0.7, cex.axis=0.7, 
        ylab="Number of participants")

@@

## (4) Regression Analysis (correctness~atom + experience + education)

@@

### Impact considering Developer Experience

@@

### Impact considering Developer Education

@@

## Impact of Individual Atoms and Hypotheses Testing

@@

  mod <- glm(subSet$correct ~ subSet$atom +  experience,family="binomial")
  print(summary(mod))
  print(prop.table(table(subSet$correct,subSet$experience),margin = 2))
}
analysis_df <- data.frame(atomDescription, chiTest, oddsRatio, 
                          oddsRatioTest, ci25, ci975, mannWhitneyTest, cliffDelta)

analysis_df <- analysis_df[order(-oddsRatio),]

colnames(analysis_df) <- c("Atom", "ChiTest", 
                           "Odds Ratio Correctness", 
                           "p-value", "CI 2.5%", "CI 97.5%", 
                           "Wilcox Test (Time)", 
                           "Cliff Delta")

xtable(analysis_df)
```
